Brief Announcement: Tight Bounds for Online Balanced Repartitioning

### 2020-02-18 paper/podc20ba.tex
Typos
CCS concepts

@@

  It remains to consider the last, unfinished phase.
  Consider the case, where the unfinished phase is also the first one.
  Then, we cannot charge $\OPT$ due to the unability to partition the components.
  Instead, we use the fact that \TAlg and $\OPT$ started with the same initial configuration.
  We charge $\OPT$ $\alpha$ for the first external $\alpha$ requests or a migration,
  and we follow the analysis regarding the unsaturated requests.
  If the input finished before the first $\alpha$ external requests, then \TAlg is optimal.
  Now, consider the case, where there are at least two phases, then we split the cost $\alpha$ charged in the penultimate phase into last two phases, and follow the analysis regarding the unsaturated requests.
  This way, the competitive ratio increases at most twofold.
\end{proof}

@@

\section{Ommited proofs}
\label{apx:omitted}

@@

\end{document}

>>>>

\ccsdesc[300]{Networks~Data center networks}
\ccsdesc[300]{Theory of computation~Unsupervised learning and clustering}

@@

  It remains to consider the last, unfinished phase.
  Consider the case, where the unfinished phase is also the first one.
  Then, we cannot charge $\OPT$ due to the inability to partition the components.
  Instead, we use the fact that \TAlg and $\OPT$ started with the same initial configuration.
  We charge $\OPT$ $\alpha$ for the first external $\alpha$ requests or a migration,
  and we follow the analysis regarding the unsaturated requests.
  If the input finished before the first $\alpha$ external requests, then \TAlg is optimal.
  Now, consider the case, where there are at least two phases, then we split the cost $\alpha$ charged in the penultimate phase into last two phases, and follow the analysis regarding the unsaturated requests.
  This way, the competitive ratio increases at most twofold.
\end{proof}

@@

\section{Omitted proofs}
\label{apx:omitted}

@@

\begin{CCSXML}
	<ccs2012>
	<concept>
	<concept_id>10003033.10003106.10003110</concept_id>
	<concept_desc>Networks~Data center networks</concept_desc>
	<concept_significance>300</concept_significance>
	</concept>
	<concept>
	<concept_id>10011007.10010940.10010971.10011120.10003100</concept_id>
	<concept_desc>Software and its engineering~Cloud computing</concept_desc>
	<concept_significance>300</concept_significance>
	</concept>
	<concept>
	<concept_id>10003752.10010070.10010071.10010074</concept_id>
	<concept_desc>Theory of computation~Unsupervised learning and clustering</concept_desc>
	<concept_significance>300</concept_significance>
	</concept>
	</ccs2012>
\end{CCSXML}

\ccsdesc[300]{Networks~Data center networks}
\ccsdesc[300]{Software and its engineering~Cloud computing}
\ccsdesc[300]{Theory of computation~Unsupervised learning and clustering}
\end{document}
